---
title: "Sentiment2"
author: "Hannah Quass"
date: "2023-10-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytext)
library(stringr)
library(lubridate)
library(textdata)
library(readxl)
library(lemon)
knit_print.data.frame <- lemon_print
```

# 1.1 Problem and data description - in report
## 1.2 Data processing
### 1.2.1 Data Preparation

```{r echo=FALSE}
houses1 <- read_excel("output.xlsx")
numericals <- c("bedrooms", "bathrooms", "erf_size", "garages", "parkings")
houses <- houses1 %>% select(-all_of(numericals))
```


- Tokenize and clean text data
```{r echo=FALSE}
replace_reg <- "[\t\r\n]"

tidy_houses <- houses %>% 
  mutate(description = str_replace_all(description, replace_reg, "")) %>% # remove tabs, newlines, etc.
  unnest_tokens(word, description, token = "words") %>% # tokenize
  filter(!word %in% stop_words$word, str_detect(word, "[a-z]")) # remove stop words
```


- Get sentiments using afinn sentiment lexicon
```{r echo=FALSE}
sentiments <- tidy_houses %>% 
  left_join(get_sentiments("afinn")) %>% # add sentiments (-5 to 5)
  mutate(sentiment = ifelse(is.na(value), 0, value)) %>% # Many sentiment values are 0!!
  select(-value)


original_sentiments <- sentiments %>%
  group_by(id) %>%
  summarize(old_sentiment = (sum(sentiment)))
```
### 1.2.2 Data Exploration

```{r echo=FALSE}
sentiments %>%
  filter(sentiment > 0) %>%
  count(word) %>%
  arrange(desc(n)) %>%
  filter(rank(desc(n)) <= 20) %>%
  ggplot(aes(reorder(word,n),n)) + geom_col() + coord_flip() + xlab("") + ggtitle("20 most common positive words")
```

```{r, echo=FALSE}
sentiments %>%
  filter(sentiment < 0) %>%
  count(word) %>%
  arrange(desc(n)) %>%
  filter(rank(desc(n)) <= 20) %>%
  ggplot(aes(reorder(word,n),n)) + geom_col() + coord_flip() + xlab("") + ggtitle("Most common negative words")
```

#### Investigating individual negative words

##### "Die"
The negative word "die" being detected is actually from "Die Laan" and "Die Boord", two Afrikaans place names in Stellenbosch - we need to change it to have a neutral sentiment

##### "Miss"
The negative word "miss" is most often used in the context: "Don't miss the opportunity to own this amazing house"

##### "Fire" and "alarm"
The context of these words is describing a house that has a fire alarm!

We need to change the sentiments of these words listed above to take their context into consideration in the analysis.

```{r echo=FALSE}
# Changing the sentiment of "Die", "fire", and "alarm" to be neutral
sentiments <- sentiments %>%
  mutate(sentiment = ifelse(word == "die", 0, sentiment))
```

```{r echo=FALSE}
change <- c("fire", "alarm")

sentiments <- sentiments %>%
  mutate(sentiment = ifelse(word %in% change, 0, sentiment))
```

#### Investigating individual positive words
##### And changing the sentiments of words not in the afinn lexicon
Drawing a random sample of descriptions to read through, I found that there were many words that clearly had a positive sentiment that the afinn lexicon did not label as such.  I manually assigned sentiments to these words.  Some examples include:
"sublime"
"exquisite"
"captivating"
"quality"
"luxury"
etc.

The assignment of these sentiment scores is clearly limited because of my subjective choices, but the subjective scores I defined still carry more meaning that a sentiment of zero would have.

```{r echo=FALSE}
# Manually change the sentiments of certain words not contained in the afinn lexicon
sent2 <- c("bespoke", "quality", "balance", "special", "symphony", "prestigious")
sent3 <- c("jaw dropping", "sublime", "showstopper", "incredible", "exceptional", "impressive")
sent4 <- c("luxurious", "unparalleled", "exquisite", "impeccable", "captivating", "luxury", "epitome", " magnificent", "spectacular")

sentiments <- sentiments %>%
  mutate(sentiment = ifelse(word %in% sent2, 2, sentiment)) %>%
  mutate(sentiment = ifelse(word %in% sent3, 3, sentiment)) %>%
  mutate(sentiment = ifelse(word %in% sent4, 4, sentiment))
```


### 1.2.3 Sentiment negation

```{r echo=FALSE, include=FALSE}
# descriptions that contain the negative word "miss":
miss_ids <- tidy_houses %>%
  group_by(id) %>%
  filter(word == "miss") %>%
  select(id)

miss_houses <- houses %>%
  filter(id %in% miss_ids$id) %>%
  select(id, description)
head(miss_houses)
```


#### Observing use cases of the word "miss":

15: Don't miss the opportunity ...
23: Don't miss your chance...
30: Don't miss out on this opportunity.
48: Don't miss out on this amazing opportunity...
271: Don't miss out on this incredible opportunity...

So what we see is that the word "miss" preceded by the word "don't" is actually a negated bigram, and I need to account for it when doing sentiment negation.

For sentiment negation the basic process was:

- Tokenise the text data by bigrams
```{r include=FALSE}
# Tokenizing by bigrams to do sentiment negation
bigrams_separated <- houses %>%
  mutate(description = str_replace_all(description, replace_reg, "")) %>%
  unnest_tokens(bigram, description, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep = " ")
```

- Get the sentiment of each word in the bigram
```{r echo=FALSE}
bigram_sentiments <- bigrams_separated %>% 
    # add sentiment for word 1
    left_join(get_sentiments("afinn"), by = c(word1 = "word")) %>%
    rename(sentiment1 = value) %>%
    mutate(sentiment1 = ifelse(is.na(sentiment1), 0, sentiment1)) %>%
    
    # add sentiment for word 2
    left_join(get_sentiments("afinn"), by = c(word2 = "word")) %>%
    rename(sentiment2 = value) %>%
    mutate(sentiment2 = ifelse(is.na(sentiment2), 0, sentiment2))
```

- Change the sentiment of the second word in a bigram by multiplying by -1 if the first word in the bigram is a negation word
```{r include=FALSE}
# Change the sentiment of bigrams containing the word "miss":
miss_sentiments <- bigram_sentiments %>% 
  filter(word2 == "miss") %>%
  # change sentiment of word2 to 0
  mutate(sentiment2 = sentiment2 * -1)
miss_sentiments <- miss_sentiments %>%
  select(-word1, -sentiment1)
```

- Negation words used:
"not"
"never"
"without"
"can't"
"won't"

```{r include=FALSE}
# Change the sentiment of negated bigrams
negation_words <- c("not", "never", "without", "can't", "won't")

# show a few
filter(bigram_sentiments, word1 %in% negation_words) %>% 
    head(50) %>% select(word1, word2, sentiment1, sentiment2) # for display purposes

```


```{r include=FALSE}
# Flip the sentiment of the second word in a negated bigram
bigrams_reversed <- bigram_sentiments %>%

    # create a variable that is the opposite of sentiment2
    mutate(opp_sentiment2 = (sentiment2 * -1)) %>%
    
    # reverse sentiment2 if word1 is a negation word
    mutate(sentiment2 = ifelse(word1 %in% negation_words, opp_sentiment2, sentiment2)) %>%
    
    # remove the opposite sentiment variable, which we don't need any more
    select(-opp_sentiment2)
```


#### Observe how the sentiments have changed after negation
```{r echo=FALSE, caption="Sentiments after negation",render=lemon_print}
bigrams_reversed %>%
  filter(word1 %in% negation_words) %>%
  filter(sentiment2 > 0)
```


- Finally, put the separated bigrams back together and update the sentiments of words that have been changed after negation.
```{r include=FALSE}
# Join the bigrams back together
bigrams_done <- bigrams_reversed %>%
  mutate(net_sentiment = (sentiment1) + (sentiment2)) %>%
  unite(bigram, word1, word2, sep = " ", remove = FALSE)

bigrams_done %>% filter(net_sentiment > 0) # display results
```


```{r include=FALSE}
# Join the results of the sentiment negation back into the main sentiments tibble
negated_ids <- bigrams_reversed %>%
  filter(word1 %in% negation_words)
```

#### Comparing how aggregate sentiment has changed after negations and manually adjusting the sentiment of individual words
```{r echo=FALSE}
# Looking at the values of aggregated sentiment again for a sanity check

new_sentiments <- sentiments %>%
  group_by(id) %>%
  summarize(new_sentiment = (sum(sentiment)))

comparison <- tibble(
  "id" = new_sentiments$id,
  "old sentiment" = original_sentiments$old_sentiment,
  "new sentiment" = new_sentiments$new_sentiment
)
```

```{r echo=FALSE, caption="Change in aggregate sentiment after processing",render=lemon_print}
head(comparison, n = 7)
```

We see that our basic sentiment analysis has significantly changed the aggregate sentiment of each house description.

## 1.3 Modelling
### 1.3.1 Developing features from the sentiments of house descriptions
Predictors:
- weighted aggregate sentiment
- number of positive words per description
- number of negative words per description
- proportion of positive words per description
- proportion of negative words per description

```{r include=FALSE}
# We will be building up the set of features in here:
features <- tibble(id = houses$id)
```


```{r include=FALSE}
sentiments_per_house <- sentiments %>%
  group_by(id) %>%
  summarize(net_sentiment = (sum(sentiment)))
head(sentiments_per_house,n = 10)
```


```{r echo=FALSE}
# Plotting aggregate sentiments
hist(sentiments_per_house$net_sentiment, 
     main = "Frequency of aggregate sentiment scores",
     xlab = "Sentiment",
     ylab = "Frequency",
     col = "lightblue",
     breaks = 30
)

```

- Note that no descriptions have a negative aggregate sentiment

Next we weight each house's sentiment score with the number of words in the description.
```{r include=FALSE}
# Weighting each house's sentiment score with the NUMBER OF WORDS in the description
# Num words in description
house_words <- houses %>%
  unnest_tokens(word, description, "words") %>%
  group_by(id) %>%
  summarise(total_words = n())

houses <- houses %>% mutate(description_length = house_words$total_words)
```


```{r}
sentiments_per_house <- sentiments_per_house %>%
  mutate(weighted_sentiment = (net_sentiment/houses$description_length))
```


```{r}
hist(sentiments_per_house$weighted_sentiment, 
     main = "Frequency of weighted aggregate sentiment scores",
     xlab = "Sentiment",
     ylab = "Frequency",
     col = "lightblue",
     breaks = 30
)
```


```{r include=FALSE}
# Add weighted sentiments to the features
features <- features %>%
  mutate(weighted_sentiment = sentiments_per_house$weighted_sentiment)
```


```{r include=FALSE}
# Add the number of positive and negative words per house to the features
pos <- sentiments %>%
  mutate(positive = ifelse(sentiment > 0, TRUE, FALSE)) %>% # boolean for pos or neg sentiment of a WORD
  group_by(id, positive) %>%
  summarize(n = n()) %>% # number of positive words per house (id grouping)
  filter(positive == TRUE) %>% # drop row of number of negative words per house
  select(id, n) %>% # select only necessary columns
  rename(num_pos_words = n)

neg <- sentiments %>%
  mutate(negative = ifelse(sentiment < 0, TRUE, FALSE)) %>%
  group_by(id, negative) %>%
  summarize(n = n()) %>%
  filter(negative == TRUE) %>%
  select(id, n) %>%
  rename(num_neg_words = n)

sentiments_summary <- tibble(id = 1:443)
sentiments_summary <- sentiments_summary %>%
  mutate(num_neg_words = ifelse(id %in% neg$id, neg$num_neg_words, 0)) %>%
  mutate(num_pos_words = ifelse(id %in% pos$id, pos$num_pos_words, 0))

```


```{r include=FALSE}
features <- features %>%
  mutate(num_pos_words = sentiments_summary$num_pos_words, num_neg_words = sentiments_summary$num_neg_words)
```


```{r include=FALSE}
# First convert price in houses to an integer
houses <- houses %>%
  mutate(price = gsub(",", "", price)) %>%
  mutate(price = as.integer(price))
```

```{r include=FALSE}
# Adding proportions of positive and negative words and price
features <- features %>%
  mutate(pos_proportion = num_pos_words/houses$description_length) %>%
  mutate(neg_proportion = num_neg_words/houses$description_length) %>%
  mutate(price = houses$price)
```

```{r include=FALSE}
# Adding description length
features <- features %>%
  mutate(description_length = houses$description_length)
```


### Observing the correlations between variables
```{r echo=FALSE}
cors <- c(
cor(features$price, features$num_pos_words),
cor(features$price, features$num_neg_words),
cor(features$price, features$pos_proportion),
cor(features$price, features$neg_proportion),
cor(features$price, features$weighted_sentiment),
cor(features$price, features$description_length)
)

feature_names <- c("num_pos_words", "num_neg_words", "pos_proportion", "neg_proportion", "weighted_sentiment", "description_length")
cors_tibble <- tibble("Feature name" = feature_names, 
                      "correlation with price" = cors)
```

```{r echo=FALSE, caption="Correlation between price and features",render=lemon_print}
cors_tibble
```

### Plotting the relationship between price and different sentiment predictors

```{r echo=FALSE}
# Plotting the relationship between price and weighted sentiment
x = (features %>% filter(price != 125000000))$price
y = (features %>% filter(price != 125000000))$weighted_sentiment

plot(x, y, main = "Relationship between price and weighted sentiment", xlab = "Price", ylab = "Weighted Sentiment", col = "blue", pch = 20, xaxt = "n")
#axis(1, at = pretty(x), labels = paste0(pretty(x) / 1000, "k"))
axis(1, at = x, labels = x)
```


```{r echo=FALSE}
# Plotting the relationship between price and number of positive and negative words
layout(matrix(c(1, 2), nrow = 1, byrow = TRUE))

x = (features %>% filter(price != 125000000))$price
y = (features %>% filter(price != 125000000))$num_pos_words
z = (features %>% filter(price != 125000000))$num_neg_words

plot(x, y, main = "Price and no. positive words", xlab = "Price", ylab = "num_pos_words", col = "blue", pch = 20, xaxt = "n")
axis(1, at = x, labels = x)

plot(x, z, main = "Price and no. negative words", xlab = "Price", ylab = "num_neg_words", col = "blue", pch = 20, xaxt = "n")
axis(1, at = x, labels = x)
```


```{r echo=FALSE}
# Plotting the relationship between price and proportions of positive and negative words
layout(matrix(c(1, 2), nrow = 1, byrow = TRUE))

x = (features %>% filter(price != 125000000))$price
y = (features %>% filter(price != 125000000))$pos_proportion
z = (features %>% filter(price != 125000000))$neg_proportion

plot(x, y, main = "Price and positive proportion", xlab = "Price", ylab = "pos_proportion", col = "blue", pch = 20, xaxt = "n")
axis(1, at = x, labels = x)

plot(x, z, main = "Price and negative proportion", xlab = "Price", ylab = "neg_proportion", col = "blue", pch = 20, xaxt = "n")
axis(1, at = x, labels = x)
```



### 1.3.2 Investigating features in different price brackets
```{r echo=FALSE}
pos <- c()
pos_p <- c()
neg <- c()
neg_p <- c()
ws <- c()
l <- c()

f1 <- features %>%
  filter(price < 3000000) %>%
  summarise(pos=mean(num_pos_words), neg=mean(num_neg_words), ws=mean(weighted_sentiment), avg_length=mean(description_length), pos_p = mean(pos_proportion), neg_p=mean(neg_proportion))
pos <- c(pos, f1$pos)
neg <- c(neg, f1$neg)
pos_p <- c(pos_p, f1$pos_p)
neg_p <- c(neg_p, f1$neg_p)
ws <- c(ws, f1$ws)
l <- c(l, f1$avg_length)

f2 <- features %>%
  filter(price >= 3000000 & price < 6000000) %>%
  summarise(pos=mean(num_pos_words),neg=mean(num_neg_words), ws = mean(weighted_sentiment),avg_length = mean(description_length), pos_p = mean(pos_proportion), neg_p=mean(neg_proportion))
pos <- c(pos, f2$pos)
neg <- c(neg, f2$neg)
pos_p <- c(pos_p, f2$pos_p)
neg_p <- c(neg_p, f2$neg_p)
ws <- c(ws, f2$ws)
l <- c(l, f2$avg_length)

f3 <- features %>%
  filter(price >= 6000000 & price < 9000000) %>%
  summarise(pos=mean(num_pos_words), neg=mean(num_neg_words), ws = mean(weighted_sentiment), avg_length = mean(description_length), pos_p = mean(pos_proportion), neg_p=mean(neg_proportion))
pos <- c(pos, f3$pos)
neg <- c(neg, f3$neg)
pos_p <- c(pos_p, f3$pos_p)
neg_p <- c(neg_p, f3$neg_p)
ws <- c(ws, f3$ws)
l <- c(l, f3$avg_length)

f4 <- features %>%
  filter(price >= 9000000 & price < 12000000) %>%
  summarise(pos=mean(num_pos_words), neg=mean(num_neg_words), ws = mean(weighted_sentiment), avg_length = mean(description_length), pos_p = mean(pos_proportion), neg_p=mean(neg_proportion))
pos <- c(pos, f4$pos)
neg <- c(neg, f4$neg)
pos_p <- c(pos_p, f4$pos_p)
neg_p <- c(neg_p, f4$neg_p)
ws <- c(ws, f4$ws)
l <- c(l, f4$avg_length)

f5 <- features %>%
  filter(price >= 12000000 & price < 15000000) %>%
  summarise(pos=mean(num_pos_words), neg=mean(num_neg_words), ws = mean(weighted_sentiment), avg_length = mean(description_length), pos_p = mean(pos_proportion), neg_p=mean(neg_proportion))
pos <- c(pos, f5$pos)
neg <- c(neg, f5$neg)
pos_p <- c(pos_p, f5$pos_p)
neg_p <- c(neg_p, f5$neg_p)
ws <- c(ws, f5$ws)
l <- c(l, f5$avg_length)

f6 <- features %>%
  filter(price >= 15000000) %>%
  summarise(pos=mean(num_pos_words), neg=mean(num_neg_words), ws = mean(weighted_sentiment), avg_length = mean(description_length), pos_p = mean(pos_proportion), neg_p=mean(neg_proportion))
pos <- c(pos, f6$pos)
neg <- c(neg, f6$neg)
pos_p <- c(pos_p, f6$pos_p)
neg_p <- c(neg_p, f6$neg_p)
ws <- c(ws, f6$ws)
l <- c(l, f6$avg_length)

features_per_bracket <- tibble(
  "Price range" = c("< 3m", "3m-6m", "6m-9m", "9m-12m", "12m-15m", "> 15m"),
  "mean positive words" = pos,
  "mean negative words" = neg,
  "mean positive proportion" = pos_p,
  "mean negative proportion" = neg_p,
  "mean weighted sentiment" = ws,
  "mean description length" = l
)
```


```{r echo=FALSE, caption="Features per price range",render=lemon_print}
features_per_bracket
```


### 1.3.3 Linear regression using only sentiment features
```{r echo=FALSE}
reg_features1 <- features %>%
  select(-id)
model1 <- lm(price ~., data = reg_features1)

summary(model1)
```

```{r echo=FALSE}
coeffs1 <- coef(model1)
#coeffs <- abs(coeffs)
sort(coeffs1, decreasing = TRUE)
```



## Linear regression using all features
```{r echo=FALSE}
# fixing the data
reg_features <- inner_join(features, houses1, by = "id")
reg_features <- reg_features %>% select(-description, -price.y) %>%
  rename(price = price.x) %>%
  mutate(bedrooms = as.integer(bedrooms)) %>%
  mutate(bathrooms = as.integer(bathrooms)) %>%
  mutate(garages = as.integer(garages)) %>%
  mutate(parkings = as.integer(parkings)) %>%
  mutate(erf_size = substr(erf_size, 1, nchar(erf_size) - 2)) %>%
  mutate(erf_size = gsub(",", "", erf_size)) %>%
  mutate(erf_size = as.integer(erf_size)) %>%
  select(-id)
```


```{r echo=FALSE}
model <- lm(price ~ ., data = reg_features)

# Summarize the model
summary(model)
```


```{r echo=FALSE}
coeffs <- coef(model)
#coeffs <- abs(coeffs)
sort(coeffs, decreasing = TRUE)
```



